Capstone Movielens Report

### 2025-02-06 reports/capstone-movielens-report.pdf-template.Rmd
Rmd Report: Datasets description started.

### Dataset

>>>>

### Datasets

``` {r , echo = FALSE}
# install.packages("pak")
pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")

```

To start with we have to generate two datasets derived from the _MovieLens_ one mentioned above:

* **edx:** we use it to develop and train our algorithms;
* **final_holdout_test:**  according to the course requirements, we use it exclusively to evaluate the _**RMSE**_ of our final algorithm.
